---
title: "Data analysis: home work #1"
author: "nick ilagnev"
date: "19 April 2016"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Lesson commands over arbuthon data

Connect external data source

```{r}
source("http://www.openintro.org/stat/data/arbuthnot.R")
```

***
Check dataset sizes, and names

```{r}
dim(arbuthnot)
names(arbuthnot)
```

***
```{r echo=F}
plot(x = arbuthnot$year, y = arbuthnot$girls, type = "l", ylab = "girls", xlab = "years", ylim = c(0,max(arbuthnot$girls)), main = "Girls over years" )
```

***
```{r echo=F}
plot(arbuthnot$year, arbuthnot$boys / (arbuthnot$boys + arbuthnot$girls) , type = "l", ylab = "boys/girls", xlab = "years", main = "Relation between girls and boys baptized over years")
```

## Data analys over actual newborn data

```{r echo = F}
source("http://www.openintro.org/stat/data/present.R")
```

Dimensions, names, and min/max years of present data set
```{r}
dim(present)
names(present)
c(min(present$year), max(present$year))
```

***
Are the present data and arbuthon on the same scale? How many times they are differ (1 - mean equal)
```{r}
mean(present$girls + present$boys) / mean(arbuthnot$girls + arbuthnot$boys)
```

***
Plot over relation between girls and boys borned in present years. As we can see on the plot boys born have tend to decrease from 1940 and then after 1975
```{r echo=F}
plot(present$year, present$boys / (present$boys + present$girls) , type = "l", ylab = "boys/girls", xlab = "years" )
```

***
In what year did we see the most total number of births in the U.S.?
```{r}
present$year[which.max(present$boys + present$girls)]
```

